---
title: "Higher Apps Practice Questions: 1.1 Fermi Estimation"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```

<hr>

For each, clearly state any **assumptions** made.

### Question 1

The population of a town is is 63,427. Estimate the number of photos in total people in the town have stored on mobile phones.

`r hide("Example Answer")`

Assume that:

- 50,000 people have photos stored on their phones. (Since not every single person will have a phone, the number chosen should be less than 63,427).

- On average a person has 300 photos stored on their phone. (Or chose some other number).

$\text{Photos stored}=50000\times300=15,000,000$

`r unhide()`

<hr>

### Question 2

Estimate the total number of cups of tea and coffee consumed by a typical person during their lifetime.

`r hide("Example Answer")`

Assume that:

- A typical person spends 60 years of their life drinking tea. (Or choose more or less, though anything approaching 90 years is probably far more than the 'typical' person).

- A typical person drinks two cups per day.

$\text{Cups drunk}=60\times 365\times2=43,800$

*Note: There aren't precisely 365 days in each year, but for the purpose of an estimation this number is perfectly reasonable to use.*

`r unhide()`

<hr>

### Question 3

Estimate the total number of text messages sent by all pupils in a secondary school during the summer holidays.

`r hide("Example Answer")`

Assume that:

- The summer lasts 7 weeks, so $7\times 6=42$ days. (Or anything from 30 days to 50 days).

- There are 700 pupils in the school. (Or anything from 100 to 3000, realistically, in Scotland).

- On average a pupil sends 5 text messages a day. (Some will send many more, some will send none).

$\text{Texts sent}=42\times 700\times5=147,000$

`r unhide()`

<hr>

