---
title: "Higher Apps Practice Questions: 3.1 Gross Pay"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```


<hr>

### Question 1

A car salesperson earns an annual salary of £36,000, as well as 6% commission on the total value of sales they make. They also receive a £150 bonus in any month during which their sales exceed £8,000.

In April, they made sales worth a total of £9,500.

Calculate their gross pay for April.

Answer: £`r fitb(3720)`

`r hide("Steps")`

Monthly salary = £`r fitb(3000)`

Commission = £`r fitb(570)`

Gross pay = £`r fitb(3720)`

`r unhide()`

<hr>

### Question 2

A travel agent earns an annual salary of £28,800, as well as 4% commission on the total value of holidays they sell. They also receive a £200 bonus in any month during which their sales exceed £12,000.

In June, they sold holidays worth a total of £11,750.

Calculate their gross pay for June.

Answer: £`r fitb(2870)`

`r hide("Steps")`

Monthly salary = £`r fitb(2400)`

Commission = £`r fitb(470)`

Bonus = £`r fitb(0)`

Gross pay = £`r fitb(2870)`

`r unhide()`

<hr>

### Question 3

A warehouse employee is paid £14.40 per hour for the first 35 hours worked each week. Any hours worked beyond 35 hours are paid at time-and-a-half. The employee also receives commission equal to 3% of the value of their weekly sales.

In one week, they worked 43 hours and made sales worth £2,800.

Calculate their gross pay for that week.

Answer: £`r fitb("760.80")`

`r hide("Steps")`

Basic pay = £`r fitb(504)`

Overtime pay = £`r fitb("172.80")`

Commission = £`r fitb(84)`

Gross pay = £`r fitb("760.80")`

`r unhide()`

<hr>

### Question 4

A fitness centre employee is paid £12.80 per hour for the first 40 hours worked each week. Any hours worked beyond 40 hours are paid at double time. The employee also receives commission equal to 6% of the value of memberships they sell.

In one week, they worked 45 hours and sold memberships worth £2,250.

Calculate their gross pay for that week.

Answer: £`r fitb(775)`

`r hide("Steps")`

Basic pay = £`r fitb(512)`

Overtime pay = £`r fitb(128)`

Commission = £`r fitb(135)`

Gross pay = £`r fitb(775)`

`r unhide()`

<hr>

