---
title: "Higher Apps Practice Questions: 3.4 Income Tax"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```


<hr>
## Scottish Income Tax Information

The following Scottish income tax rates apply:

| Band | Taxable income | Scottish tax rate |
|---|---:|---:|
| Personal Allowance | Up to £12,570 | 0% |
| Starter rate | £12,570 to £15,397 | 19% |
| Basic rate | £15,397 to £27,491 | 20% |
| Intermediate rate | £27,491 to £43,662 | 21% |
| Higher rate | £43,662 to £75,000 | 42% |
| Advanced rate | £75,000 to £125,140 | 45% |
| Top rate | Over £125,140 | 48% |

Like National Insurance, income tax is calculated using tax bands. This means that different parts of a person’s taxable income may be taxed at different rates. Unlike National Insurance, the values in the income tax bands are based on annual income.

Income tax is calculated using a person’s taxable pay:

\[
\text{Taxable pay}
=
\text{Gross pay}
-
\text{Pension contributions}
\]

National Insurance contributions are not deducted when calculating taxable pay.

---

### Question 1

Hannah earns an annual salary of £34,800 and pays £2,400 into her workplace pension scheme each year.

She pays £2,680.32 per year in National Insurance contributions.

Calculate the annual income tax Hannah should pay.

Answer: £`r fitb(3986.82)`

`r hide("Worked solution")`

First, calculate Hannah’s taxable pay.

\[
£34,800-£2,400=£32,400
\]

The National Insurance contribution is not deducted when calculating taxable pay.

Hannah pays no tax on the first £12,570 because this is her Personal Allowance.

#### Starter rate

The amount taxed at 19% is:

\[
£15,397-£12,570=£2,827
\]

Tax paid at the starter rate:

\[
£2,827\times 0.19=£537.13
\]

#### Basic rate

The amount taxed at 20% is:

\[
£27,491-£15,397=£12,094
\]

Tax paid at the basic rate:

\[
£12,094\times 0.20=£2,418.80
\]

#### Intermediate rate

Hannah’s remaining taxable income is:

\[
£32,400-£27,491=£4,909
\]

Tax paid at the intermediate rate:

\[
£4,909\times 0.21=£1,030.89
\]

#### Total annual income tax

\[
£537.13+£2,418.80+£1,030.89=£3,986.82
\]

Therefore, Hannah should pay:

\[
\boxed{£3,986.82}
\]

in income tax each year.

`r unhide()`

---

### Question 2

An engineer earns an annual salary of £64,800 and does not pay any money into a pension fund.

They pay £277.50 each month in National Insurance contributions.

Calculate their monthly income tax payments.

Answer: £`r fitb(1269.15)`

`r hide("Worked solution")`

The engineer does not make any pension contributions, so their taxable pay is:

\[
£64,800
\]

The National Insurance contribution is not deducted when calculating taxable pay.

The engineer pays no tax on the first £12,570 because this is their Personal Allowance.

#### Starter rate

The amount taxed at 19% is:

\[
£15,397-£12,570=£2,827
\]

Tax paid at the starter rate:

\[
£2,827\times 0.19=£537.13
\]

#### Basic rate

The amount taxed at 20% is:

\[
£27,491-£15,397=£12,094
\]

Tax paid at the basic rate:

\[
£12,094\times 0.20=£2,418.80
\]

#### Intermediate rate

The amount taxed at 21% is:

\[
£43,662-£27,491=£16,171
\]

Tax paid at the intermediate rate:

\[
£16,171\times 0.21=£3,395.91
\]

#### Higher rate

The remaining taxable income is:

\[
£64,800-£43,662=£21,138
\]

Tax paid at the higher rate:

\[
£21,138\times 0.42=£8,877.96
\]

#### Total annual income tax

\[
£537.13+£2,418.80+£3,395.91+£8,877.96
=
£15,229.80
\]

To calculate the monthly payment, divide the annual tax by 12.

\[
£15,229.80\div 12=£1,269.15
\]

Therefore, the engineer’s monthly income tax payment is:

\[
\boxed{£1,269.15}
\]

`r unhide()`

---

### Question 3

Rory earns an annual salary of £82,000 and pays £6,000 into his workplace pension scheme each year.

Calculate the annual income tax Rory should pay.

Answer: £`r fitb("19963.80")`

`r hide("Worked solution")`

First, calculate Rory’s taxable pay.

\[
£82,000-£6,000=£76,000
\]

Rory pays no tax on the first £12,570 because this is his Personal Allowance.

#### Starter rate

The amount taxed at 19% is:

\[
£15,397-£12,570=£2,827
\]

Tax paid at the starter rate:

\[
£2,827\times 0.19=£537.13
\]

#### Basic rate

The amount taxed at 20% is:

\[
£27,491-£15,397=£12,094
\]

Tax paid at the basic rate:

\[
£12,094\times 0.20=£2,418.80
\]

#### Intermediate rate

The amount taxed at 21% is:

\[
£43,662-£27,491=£16,171
\]

Tax paid at the intermediate rate:

\[
£16,171\times 0.21=£3,395.91
\]

#### Higher rate

The amount taxed at 42% is:

\[
£75,000-£43,662=£31,338
\]

Tax paid at the higher rate:

\[
£31,338\times 0.42=£13,161.96
\]

#### Advanced rate

Rory’s remaining taxable income is:

\[
£76,000-£75,000=£1,000
\]

Tax paid at the advanced rate:

\[
£1,000\times 0.45=£450
\]

#### Total annual income tax

\[
£537.13+£2,418.80+£3,395.91+£13,161.96+£450
=
£19,963.80
\]

Therefore, Rory should pay:

\[
\boxed{£19,963.80}
\]

in income tax each year.

`r unhide()`

