---
title: "Higher Apps Practice Questions: 3.5 Net Pay"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```

---

### Question 1

Morgan earns an annual salary of £42,500. They pay annual Income Tax of £5,840, annual National Insurance contributions of £2,316, and annual workplace pension contributions of £2,125.

Calculate Morgan’s annual net pay.

Answer: £`r fitb(32219)`

`r hide("Worked solution")`

Total annual deductions = £`r fitb(10281)`

Annual net pay = £`r fitb(32219)`

`r unhide()`

---

### Question 2

Aisha earns £2,850 per month. Her monthly Income Tax is £372.40, and her monthly National Insurance contribution is £146.80. She also contributes 4% of her gross monthly pay to her workplace pension.

Calculate Aisha’s monthly net pay.

Answer: £`r fitb("2216.80")`

`r hide("Worked solution")`

Monthly pension contribution = £`r fitb(114)`

Total monthly deductions = £`r fitb("663.20")`

Monthly net pay = £`r fitb("2216.80")`

`r unhide()`

---

### Question 3

Lewis earns an annual salary of £36,600. His annual Income Tax has been calculated as £4,280, and he pays annual National Insurance contributions of £1,795. He also contributes 6% of his gross annual salary to his workplace pension.

Calculate Lewis’s annual net pay.

Answer: £`r fitb(28329)`

`r hide("Worked solution")`

Annual pension contribution = £`r fitb(2196)`

Total annual deductions = £`r fitb(8271)`

Annual net pay = £`r fitb(28329)`

`r unhide()`
