---
title: "Higher Apps Practice Questions: 3.3 National Insurance"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```


<hr>

## National Insurance Information

You begin paying National Insurance once you earn more than £1,048 a month. This is the threshold for the 2025/26 tax year.

For payslips dated between 6 April 2025 and 5 April 2026, you pay:

- 8% of monthly earnings between £1,048 and £4,189;
- 2% of monthly earnings above £4,189.

National Insurance is calculated using a person’s salary before deductions such as pension contributions.

---

### Question 1

Aisha earns a monthly salary of £3,650.

Calculate her total annual National Insurance contributions.

Answer: £`r fitb(2497.92)`

`r hide("Worked solution")`

Aisha earns less than £4,189 per month, so she pays National Insurance at 8% on the part of her salary above £1,048.

Monthly earnings subject to National Insurance:

\[
£3,650-£1,048=£2,602
\]

Monthly National Insurance contribution:

\[
£2,602\times 0.08=£208.16
\]

Annual National Insurance contribution:

\[
£208.16\times 12=£2,497.92
\]

Therefore, Aisha’s total annual National Insurance contributions are:

\[
\boxed{£2,497.92}
\]

`r unhide()`

---

### Question 2

Marcus earns an annual salary of £60,120. He pays £4,560 into his pension fund each year.

Calculate his monthly National Insurance contribution.

Answer: £`r fitb("267.70")`

`r hide("Worked solution")`

National Insurance is calculated before the pension contribution is deducted. Therefore, the pension contribution does not affect the calculation.

Marcus’s monthly salary is:

\[
£60,120\div 12=£5,010
\]

Marcus pays 8% on his monthly earnings between £1,048 and £4,189.

Earnings in the 8% band:

\[
£4,189-£1,048=£3,141
\]

National Insurance at 8%:

\[
£3,141\times 0.08=£251.28
\]

Marcus also pays 2% on his monthly earnings above £4,189.

Earnings in the 2% band:

\[
£5,010-£4,189=£821
\]

National Insurance at 2%:

\[
£821\times 0.02=£16.42
\]

Total monthly National Insurance contribution:

\[
£251.28+£16.42=£267.70
\]

Therefore, Marcus’s monthly National Insurance contribution is:

\[
\boxed{£267.70}
\]

`r unhide()`

---

### Question 3

Euan earns a monthly salary of £980.

State his monthly National Insurance contributions.

Answer: £`r fitb(0)`

`r hide("Worked solution")`

A person begins paying National Insurance once they earn more than £1,048 per month.

Euan earns:

\[
£980
\]

Since:

\[
£980<£1,048
\]

Euan does not pay any National Insurance each month.


Therefore, Euan’s monthly National Insurance contributions are:

\[
\boxed{£0}
\]

`r unhide()`

