---
title: "Higher Apps Practice Questions: 3.2 Pensions"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```


<hr>

### Question 1

Bob earns an annual salary of £32,400 and he pays 2.8\% of her earnings into his pension fund. His employer also contributes 5.4\% of the same earnings into his pension fund. Calculate Bob's \textbf{monthly} taxable pay.

Answer: £`r fitb("2624.40")`

`r hide("Steps")`

Monthly salary = £`r fitb(2700)`

Monthly pension contribution = £`r fitb("75.60")`

Monthly taxable pay = £`r fitb("2624.40")`

`r unhide()`

<hr>

### Question 2

Callum earns an annual salary of £39,600. He pays 3.5% of his earnings into his pension fund. His employer also contributes 5.8% of the same earnings.

Calculate Callum’s monthly taxable pay after his pension contribution has been deducted.

Answer: £`r fitb("3184.50")`

`r hide("Steps")`

Monthly salary = £`r fitb(3300)`

Monthly pension contribution = £`r fitb("115.50")`

Monthly taxable pay = £`r fitb("3184.50")`

`r unhide()`

<hr>

### Question 3

Priya earns a monthly salary of £2,750. She pays 5.2% of her earnings into her pension fund. Her employer also contributes 7.3% of the same earnings.

Calculate the total amount paid into Priya’s pension fund annually.

Answer: £`r fitb(4125)`

`r hide("Steps")`

Her monthly contribution = £`r fitb(143)`

Her employer's monthly contribution  = £`r fitb(200.75)`

Total monthly contribution  = £`r fitb(343.75)`

Total annual contribution = £`r fitb(4125)`

`r unhide()`

<hr>

### Question 4

Lewis earns an annual salary of £46,800. He pays 4.2% of his earnings into his pension fund. His employer also contributes 6.9% of the same earnings.

Calculate Lewis’s monthly taxable pay after his pension contribution has been deducted.

Answer: £`r fitb("3736.20")`

`r hide("Steps")`

Monthly salary = £`r fitb(3900)`

Monthly pension contribution = £`r fitb("163.80")`

Monthly taxable pay = £`r fitb("3736.20")`

`r unhide()`

<hr>

