---
title: "3 Practice Questions - Probability"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```

## Question 1

A shop sells different packs of fruit, with some grown in the UK and some imported. The table below shows the packs in stock.

|  | Apples | Plums | Strawberries | 
|:----:|:----:|:----:|:----:|
| UK-grown | 12 | 9 | 11 |
| Imported | 7 | 8 | 3 |

A pack of fruit is chosen from those in stock at random.

#### (a)

The probability that the pack is of **apples which were imported** is `r fitb(7)` out of `r fitb(50)`.

The probability that the pack is of **apples which were imported** is `r fitb(7)` out of `r fitb(50)`.

The probability that the pack is of **apples which were imported** is `r fitb(7)` out of `r fitb(50)`.

#### (b)

The probability that the pack is **not apples**, as a **decimal**, is `r fitb(0.62)`.

The probability that the pack is **not apples**, as a **decimal**, is `r fitb(0.62)`.

The probability that the pack is **not apples**, as a **decimal**, is `r fitb(0.62)`.

#### (c)

The probability that the pack chosen is **plums or UK-grown**, as a **percentage**, is `r fitb(80)`%. 

The probability that the pack chosen is **plums or UK-grown**, as a **percentage**, is `r fitb(80)`%. 

The probability that the pack chosen is **plums or UK-grown**, as a **percentage**, is `r fitb(80)`%. 
