---
title: "Practice Questions - Probability"
output: webexercises::webexercises_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(webexercises)
```


```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple")
```

---

## Question 1

A large garage employs a mix of full-time and part-time staff, made up of both mechanics and office workers.

|  | Mechanic | Office |
|:----:|:----:|:----:|
| Full-time | 4 | 3 |
| Part-time | 1 | 2 |

A member of staff is chosen at random to be interviewed about how they like working at the garage.

#### (a) Give each probability as a **fraction**.

The probability the member of staff is **a part-time mechanic** is `r fitb(1)` out of `r fitb(10)`.

The probability the member of staff is **a full-time office worker** is `r fitb(3)` out of `r fitb(10)`.


#### (b) Give each probability as a **decimal**.

The probability the member of staff is **full-time** is `r fitb(c("0.7","0.70"))`.

The probability the member of staff is **mechanic** is `r fitb(c("0.5","0.50"))`.


#### (c) Give each probability as a **percentage**.

P(mechanic **or** part-time) =  `r fitb(70)`%. 

P(office worker **or** full-time) = `r fitb(90)`%. 

---

## Question 2

A shop sells different packs of fruit, with some grown in the UK and some imported. The table below shows the packs in stock.

|  | Apples | Plums | Strawberries | 
|:----:|:----:|:----:|:----:|
| UK-grown | 12 | 9 | 11 |
| Imported | 7 | 8 | 3 |

A pack of fruit is chosen from those in stock at random.

#### (a) Give each probability as a **fraction**.

The probability that the pack is of **apples which were imported** is `r fitb(7)` out of `r fitb(50)`.

The probability that the pack is of **strawberries which were not imported** is `r fitb(11)` out of `r fitb(50)`.

The probability that the pack is of **plums** is `r fitb(17)` out of `r fitb(50)`.

#### (b) Give each probability as a **decimal**.

The probability that the pack is **UK-grown** is `r fitb(0.64)`.

The probability that the pack is **not apples** is `r fitb(0.62)`.

The probability that the pack is **imported but not plums** is `r fitb(c("0.20","0.2"))`.

#### (c) Give each probability as a **percentage**.

The probability that the pack chosen is **plums or UK-grown** is `r fitb(80)`%. 

The probability that the pack chosen is **apples or imported** is `r fitb(60)`%. 

The probability that the pack chosen is **plums or strawberries** is `r fitb(62)`%. 

---

## Question 3

#### (a)

The probability that a randomly selected car parked on a town centre street is parked without a ticket is 15%. If there are 80 cars parked on a street, calculate how many would be expected to be parked without a ticket.

Answer: `r fitb(12)` cars.

#### (b)


A student sits a multiple choice exam containing 40 questions, each with possible answers from A to E.

If the student guesses a choice at random, the probability they will get it correct is `r fitb(1)` in `r fitb(5)`.

If they guess every question, calculate how many questions they might expect to get correct.

Answer: `r fitb(8)` questions.

#### (c)

A factory makes light bulbs. The probability that a newly produced light bulb will not work due to some flaw in the production process is known to be 2%.

Each hour, the factory makes 300 bulbs. Calculate the expected number of non-working bulbs made by the factory during an eight-hour shift.

Answer: `r fitb(48)` bulbs.
